Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-05-08 PAPER.tex
Tue May  8 17:15:34 EDT 2018

The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, error estimation, and bias) that are essential to investigate 
for a robust 21\,cm power spectrum analysis. We also highlight four power spectrum techniques (fringe-rate filtering, weighting, bootstrapping, jackknife testing) and their trade-offs, potential 
pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER. In this study we use a subset of the PAPER-64 data to illustrate our revised analysis methods, while a companion paper, Kolopanis et al. (\textit{submitted}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.

@@

\begin{center}
Power Spectrum Themes
\end{center}

A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power 
spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target \textit{cosmological} signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a 21\,cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Additionally, accurate error estimation is crucial for the comparison of results to theoretical models. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving that a bias is an EoR detection may be the most difficult challenge for 21\,cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}

@@

\begin{equation}
\label{eq:qhat}
\widehat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}.
\end{equation}
Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier transforms them, while also converting from Jy to 
Kelvin and taking into account cosmological scalings. It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the 
Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes). $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as 
an example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $
\textbf{R} \equiv \textbf{I}$, the identity matrix.

@@

We now apply these lessons to data from the PAPER experiment, using a subset of the PAPER-64 dataset from
\citetalias{ali_et_al2015}) in order to illustrate our revised analysis pipeline.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0cm 3cm 0cm 3cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
	\caption{The PAPER-64 antenna layout. We use only $10$ of the $30$ m East/West baselines for the analysis in this 
paper (i.e. a subset of the shortest horizontal spacings).}
	\label{fig:ant_layout}
\end{figure}

@@

For the analysis in this paper, we use $8.1$ hours of LST, namely an RA range of $0.5$-$8.6$ hours (\citetalias{ali_et_al2015} uses a slightly longer RA 
range of $0$-$8.6$ hours; we found that some early LSTs were more severely foreground contaminated). We also use only $10$ baselines, a subset of the $51$ total East/West baselines used in \citetalias{ali_et_al2015}. All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}. In the case study in this paper, we only use one baseline type instead of the three as in 
\citetalias{ali_et_al2015}, but Kolopanis et al. (\textit{submitted}) uses all baselines presented in \citetalias{ali_et_al2015}.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
	\caption{Illustration of the power spectrum amplitude of various power spectrum terms as a function of injected EoR power level summed into the 
data. Left: The empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015}. The output power spectrum ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation 
\eqref{eq:crossterm} are shown in blue, red, and green. The dotted diagonal black line indicates perfect 1:1 input-to-output mapping (no signal loss). The details of the simulation used to generate the figure is explained in Section 
\ref{sec:Practice}; here we sample a larger $P_{\rm in}$ range and fit smooth polynomials to our data points to make an illustrative example.  The gray 
horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power). The green signal-signal 
component is the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
regime where cross-correlations between injection and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like 
term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$. However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect 
$\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
the data-only power spectrum value) and the black curve (which exhibits $\sim$$4$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
	\label{fig:sigloss_terms}
\end{figure*}

@@

By-eye inspection of the transfer function in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
\widehat{\textbf{P}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{5} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{9} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$. For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$.

@@

The loss-corrected power spectrum limit for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (solid red), which we can compare to the original lossy result (dashed red). %There are a few important checks to examine. First, we see that the uniform-weighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels. This is an important check, as we expect no signal loss for this case. Any difference here would indicate an error in the pipeline or discrepancy in the range of data included. Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction. 
Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (which is shown three ways: black and gray points are positive and negative power spectrum values, respectively, with $2\sigma$ error bars, the solid blue is the upper limit on the EoR signal using the full signal injection framework, and the shaded gray is the power spectrum values with thermal noise errors). We elaborate on this point in the next section, as well as investigate alternate 
weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of the EoR signal.

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_data.pdf}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data.pdf}
	\caption{The power spectrum of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using empirical inverse covariance weighting. Shown for comparison is the lossy limit prior to signal loss estimation (dashed red). The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:PSSense}. Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions). The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.}
\label{fig:ps2_data}
\end{figure*}

@@

We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
eigenspectrum and effectively de-coupling the lowest-valued eigenmodes from the data, which converge to the true eigenspectrum the slowest and are often EoR-dominated) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is the full inverse 
covariance estimator). The power spectrum results for one $k$-value, both before and after signal loss 
estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
becomes more aggressive (dashed red). In other words, more EoR-dominated fluctuations are being overfit and 
subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
increases with the number of down-weighted modes (solid red). The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum. \citet{switzer_et_al2013} took a similar approach in determining the optimal number of modes to down-weight in GBT data, finding similar trends and noting that removing too few modes is limited by residual foregrounds and removing too many modes is limited by large error bars and signal loss.

Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting 
is beneficial compared to uniform weighting (blue). In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes. We see in Figure \ref{fig:sigloss_modeloop} that this occurs when 
only the $\sim2$ highest-valued eigenmodes are down-weighted and the rest are given equal weights. For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.

We also saw in Section \ref{sec:otherweight} how adding the identity matrix to the empirical covariance can minimize signal loss. We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}. The dashed red and solid red lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$. We parameterize this ``regularization strength" parameter as $\gamma$, namely $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + \gamma$Tr$(\widehat{\textbf{C}})\textbf{I}$. From this plot we see that only a small percentage of Tr($\widehat{\textbf{C}})$ is needed to significantly reduce loss. We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the red curves will approach the uniform-weighted case. We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear `minimum' that produces the least loss.

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.pdf}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (dashed red) and after (solid red) signal loss estimation via our signal injection framework as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. the full inverse 
covariance estimator). Over $\sim3$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting. Bottom: Power spectrum upper limits before (dashed red) and after (solid red) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e. very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$). Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (blue) and inverse variance 
weighted case (black); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as green. In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
	\label{fig:sigloss_modeloop}
\end{figure*}

In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
in both panels and represents a third regularization technique. This line (black) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
matrix element-wise to $\widehat{\textbf{C}}$). This result is single-valued and not a function of the horizontal axis. We see that all three regularization schemes shown (solid red, dashed red, black) perform similarly at 
their best (i.e. when $\sim2$ eigenmodes are down-weighted in the case of the solid red curve). However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.035$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$. We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$. We also note that all of the regularizations described here perform similarly to the uniformly weighted case. However, we find that the regularization of empirical covariances does outperform the uniform weighted case for redshift bins in which there are stronger foregrounds, as presented in Kolopanis et al. (\textit{submitted}).

The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
\ref{fig:ps1_data}. Again, the solid red curve represents our upper limit on the EoR signal using the full signal injection framework. The uniform weighted case is shown as the black and gray points, which correspond to positive and negative power spectrum values respectively (with 
$2\sigma$ errors bars). It is also shown as an upper limit using the signal injection framework (solid blue). Finally, the gray shaded regions combine the measured uniform weighted power spectrum values and the thermal noise. We show this power spectrum result as one example of how a simple regularization can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case. In Kolopanis et al. (\textit{submitted}), multiple redshifts are explored and found to benefit from weighting differently.

>>>>

The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, error estimation, and bias) that are essential to investigate 
for a robust 21\,cm power spectrum analysis. We also highlight four power spectrum techniques (fringe-rate filtering, weighting, bootstrapping, jackknife testing) and their trade-offs, potential 
pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
from the lessons learned. A companion paper, Kolopanis et al. (\textit{submitted}), builds off of the methods in this paper to present PAPER-64 results for multiple redshifts and baseline types.

@@

%\begin{center}
%Power Spectrum Themes
%\end{center}
%
%A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power 
%spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
%a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target \textit{cosmological} signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a 21\,cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Additionally, accurate error estimation is crucial for the comparison of results to theoretical models. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving that a bias is an EoR detection may be the most difficult challenge for 21\,cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}

@@

\begin{equation}
\label{eq:qhat}
\widehat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}.
\end{equation}

The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded in $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$.  In practice, it also implements a transform of the frequency-domain visibilities to 
$\mathbf{k}$ space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.

their Fourier conjugates, and converts from Jy to Kelvin and . It is formally evaluated as  (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the 
Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes). $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as 
an example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $
\textbf{R} \equiv \textbf{I}$, the identity matrix.

@@

We now apply these lessons to data from the PAPER experiment to make a new analysis of the PAPER-64 dataset originally presented in 
\citetalias{ali_et_al2015} and obtain a revised power spectrum estimate.

@@

\begin{figure}
	\centering
	\includegraphics[trim={0cm 3cm 0cm 3cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 
paper (i.e. the shortest horizontal spacings).}
	\label{fig:ant_layout}
\end{figure}

@@

For our revised analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citetalias{ali_et_al2015} uses a slightly longer RA 
range of $0$-$8.6$ hours; we found that some early LSTs were more severely foreground contaminated). All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}. In the case study in this paper, we only use one baseline type instead of the three as in 
\citetalias{ali_et_al2015}, but Kolopanis et al. (\textit{submitted}) uses all baselines presented in \citetalias{ali_et_al2015}.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
	\caption{Illustration of the power spectrum amplitude of various power spectrum terms as a function of injected EoR power level summed into the 
data. Left: The empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015}. The output power spectrum ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation 
\eqref{eq:crossterm} are shown in blue, red, and green. The dotted diagonal black line indicates perfect 1:1 input-to-output mapping (no signal loss). The details of the simulation used to generate the figure is explained in Section 
\ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.  The gray 
horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power). The green signal-signal 
component is the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
regime where cross-correlations between injection and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like 
term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$. However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect 
$\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
the data-only power spectrum value) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
	\label{fig:sigloss_terms}
\end{figure*}

@@

By-eye inspection of the transfer function in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
\widehat{\textbf{P}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{4} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{8} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$. For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$.

@@

The loss-corrected power spectrum result for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points). %There are a few important checks to examine. First, we see that the uniform-weighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels. This is an important check, as we expect no signal loss for this case. Any difference here would indicate an error in the pipeline or discrepancy in the range of data included. Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction. 
Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (blue dashed). We elaborate on this point in the next section, as well as investigate alternate 
weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of the EoR signal.

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_data.pdf}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data.pdf}
	\caption{The power spectrum of PAPER-64 data, weighted by an inverse covariance estimator. The power spectra values pre-signal loss estimation are shown as black and gray points (positive and negative values, respectively, 
with $2\sigma$ error bars). The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation. The dashed blue line is the uniform-weighted power 
spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
	\label{fig:ps2_data}
\end{figure*}

@@

We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
eigenspectrum and effectively de-coupling the lowest-valued eigenmodes from the data, which converge to the true eigenspectrum the slowest and are often EoR-dominated) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is the full inverse 
covariance estimator). The power spectrum results for one $k$-value, both before and after signal loss 
estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
becomes more aggressive (gray curve). In other words, more EoR-dominated fluctuations are being overfit and 
subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
increases with the number of down-weighted modes (black curve). The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum. \citet{switzer_et_al2013} took a similar approach in determining the optimal number of modes to down-weight in GBT data, finding similar trends and noting that removing too few modes is limited by residual foregrounds and removing too many modes is limited by large error bars and signal loss.

Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting 
is beneficial compared to not weighting (blue dashed line). In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes. We see in Figure \ref{fig:sigloss_modeloop} that this occurs when 
only the $\sim2$ highest-valued eigenmodes are down-weighted and the rest are given equal weights. For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.

We also saw in Section \ref{sec:otherweight} how adding the identity matrix to the empirical covariance can minimize signal loss. We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}. The gray and black lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$. We parameterize this ``regularization strength" parameter as $\gamma$, namely $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + \gamma$Tr$(\widehat{\textbf{C}})\textbf{I}$. From this plot we see that only a small percentage of Tr($\widehat{\textbf{C}})$ is needed to significantly reduce loss. We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the uniform-weighted case. We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear `minimum' that produces the least loss.

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.pdf}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. the full inverse 
covariance estimator). Over $\sim3$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting. Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e. very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$). Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green. In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
	\label{fig:sigloss_modeloop}
\end{figure*}

In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
in both panels and represents a third regularization technique. This line (red) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
matrix element-wise to $\widehat{\textbf{C}}$). This result is single-valued and not a function of the horizontal axis. We see that all three regularization schemes shown (black solid, black dashed, red) perform similarly at 
their best (i.e. when $\sim2$ eigenmodes are down-weighted in the case of the black solid curve). However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.035$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$. We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$. We also note that all of the regularizations described here perform similarly to the uniformly weighted case. However, we find that the regularization of empirical covariances does outperform the uniform weighted case for redshift bins in which there are stronger foregrounds, as presented in Kolopanis et al. (\textit{submitted}).

A revised PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
\ref{fig:ps1_data}. Again, the dashed black curve represents our upper limit on EoR, post-signal loss estimation. Black and gray points correspond to positive and negative power spectrum values respectively (pre-signal loss estimation), with 
$2\sigma$ errors bars. Also plotted are the uniform-weighted power spectrum upper limit (dashed blue) and theoretical prediction of 
noise (solid green). In Kolopanis et al. (\textit{submitted}), multiple baselines are used in the analysis to produce a $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$, 
a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.
